---
title: "R Notebook"
output: html_notebook
---
# Install Packages
```{r}
install.packages("tidyverse", dependencies = TRUE)
install.packages("ggthemes", dependencies = TRUE)
```
# Load Packages
```{r}
library(tidyverse)
library(ggplot2)
library(ggthemes)
```
# Import Data
```{r}
assignment4 = read_csv("a4_data.csv")
```
# Rows and Columns
```{r}
nrow(assignment4)
ncol(assignment4)
```
There are 3700 rows and 12 columns in this data file.

# Unique Participants and Trials
```{r}
subject_IDs = assignment4 %>%
  pull(subject) %>%
  unique()
length(subject_IDs)

assignment4 %>%
  group_by(subject)%>%
  count()
```
There are 37 subjects included in this data file. Each subject completed 100 trials.

# Levels of Variables
```{r}
prime_and_state = assignment4 %>%
  mutate(prime_condition = as.factor(prime_condition), state = as.factor(state))

levels(prime_and_state %>% pull(prime_condition))
levels(prime_and_state %>% pull(state))
```
The variable "prime condition" has 4 levels: "both," "phonological," "semantic," and "unrelated." The variable "state" also has 4 levels: " dontknow," "know," "other," and "tipoftongue."

# Subsets of Columns
```{r}
prime_information = assignment4 %>%
  select(subject, prime_condition)
```

# Subsets of Rows
```{r}
phonological = assignment4 %>%
  filter(prime_condition == "phonological" & accuracy == 1 )
```

# Summarizing Accuracy per Subject
```{r}
subject_acc = assignment4 %>%
  group_by(subject) %>%
  summarise(mean = mean(accuracy))
```

# Summarizing Accuracy per Prime Condition
```{r}
prime_acc = assignment4 %>%
  group_by(prime_condition) %>%
  summarise(mean = mean(accuracy), sd = sd(accuracy))
```

# Histogram of Subject Accuracy
```{r}
subject_acc %>% 
  
ggplot(aes(x = mean)) +
  geom_histogram(binwidth = .2,
  fill = "pink", color = "black", 
  position = "identity")+
  theme_few()+
xlab("Mean Accuracy") + 
ylab ("Count")+
ggtitle("Histogram of Subject Mean Accuracy")
```
# Bar Plot of Prime Condition
```{r}
prime_acc %>%

ggplot(aes(x = prime_condition, y = mean)) +
  geom_bar(stat = "identity", fill = "navy", color = "black" ) +
  theme_clean() +
  xlab("Prime Condition") +
  ylab("Mean Accuracy") +
  ggtitle("Mean Accuracy by Prime Condition")
  
```

# Data Interpretation
"Semantic" primes lead to faster response times than "phonological," "unrelated," and "both". "Phonological" primes lead to the slowest response times while "both" and "unrelated" led to very similar response times

# EC: Summarizing Accuracy per Prime Condition and State 
```{r}
state_prime_acc = assignment4 %>%
  group_by(state, prime_condition)%>%
  summarise(mean = mean(accuracy))
```
# EC: Bar Plot of Prime Condition and State
```{r}
state_prime_acc%>%
  ggplot(aes(x = prime_condition, y = mean, fill = state)) +
  geom_col(position = "dodge") +
  theme_clean()+
  labs(x = "Prime Condition", y = "Mean Accuracy", title = "Mean Accuracy By Prime Condition and State")
```

